---
title: "Getting Started with binomial Package"
author: "Wenkai Yang"
date: "`r Sys.Date()`"
output:  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## Binomial random variable

The package `"binomial"` is an implementation for creating a binomial object with specified total number of trials and success probabiity, and summarize its statistics such as mean, variance, etc. Also, it can help to summarize and visualize the probability distribution and cumulative probability distribution.



## Creating a binomial object

The first step is to create a `"binvar"` object with the function `bin_variable()`:

```{r}
bin1 <- bin_variable(trials = 10, prob = 0.3)
bin1
```


You can change to other values of arguments `trials` and `prob`:



## Summary of statistics

Then you can get the a summary of values of mean, variance, mode, skewness and kurtosis of this object.

```{r}
binsum1 <- summary(bin1)
binsum1
```


### Other useful functions

If you are only interested in the value of mean (or variance, or other statistic), you can use other functions inside inside this package.

```{r}
bin_mean(10, 0.3)
## [1] 3
bin_variance(10, 0.3)
## [1] 2.1
bin_mode(10, 0.3)
## [1] 3
bin_skewness(10, 0.3)
## [1] 0.2760262
bin_kurtosis(10, 0.3)
## [1] -0.1238095
```



## Probability distribution

The other thing this package can do is give you summaries and plots of probability distribution and cumulative probability distribution, using functions `"bin_choose()"`, `"bin_probability()"`, `"bin_distribution()"`, `"bin_cumulative()"` and generic function `"plot()"`.

```{r}
# choosing k from n
bin_choose(n = 10, k = 5)
```


```{r}
# probabilities of getting 3 or less successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 0:3, trials = 5, prob = 0.5)
```

```{r}
# binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
# plot probability distribution 
plot(dis1)
```

```{r}
# binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
# plot cumulative probability distribution 
plot(dis2)
```
